---
title: "liftr"
subtitle: "With custom french template"
author: 
  - "Nan Xiao, Nicolas Roelandt"
classname: "Custom project"
formation: "Master degree"
parcours: 'mutatis mutandis.'
responsable: "Pr.Charles Xavier"

date: "`r Sys.Date()`"
output:
  rmarkdown::pdf_document:
    #template: /data/article.tex
    template: /data/etude/etude.tex
    toc: true
    number_sections: true
    keep_tex : true
    latex_engine: xelatex
    fig_width: 7
    fig_height: 6
    fig_caption: true
    #includes:
    #  in_header: /data/templates/chunks/header.tex
    #  before_body: /data/templates/chunks/doc_prefix.tex
    #  after_body: /data/templates/chunks/doc_suffix.tex

mainfont: Linux Libertine O
sansfont: Linux Biolinum O
maincolor: rstudioblue
fontsize: 11pt
lang: fr
liftr:
  from: "rocker/tidyverse:latest"
  maintainer: "Nan Xiao"
  email: "me@nanx.me"
  pandoc: false
  texlive: true
  sysdeps:
    - texlive-xetex
    - texlive-luatex
    - texlive-latex-recommended
    - fonts-linuxlibertine
    - texlive-lang-french
  cran:
    - nycflights13
  include: "DockerfileSnippet"
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knit_hooks$set(document = function(x) {sub('\\usepackage[]{color}', '\\usepackage{xcolor}', x, fixed = TRUE)})

```
\clearpage

pdf_document customisation:

http://rmarkdown.rstudio.com/pdf_document_format.html


# section
## subsection
### subsubsection
#### paragraph
##### subparagraph
###### subsubparagraph (What ? You wanted more ?)

An ionocraft[^ionocraft] or ion-propelled aircraft (commonly known as a lifter or hexalifter) is a device that uses an electrical electrohydrodynamic (EHD) phenomenon to produce thrust in the air without requiring any combustion or moving parts.

[^ionocraft]:
    [https://en.wikipedia.org/wiki/Ionocraft](https://en.wikipedia.org/wiki/Ionocraft)






# Images and footnotes

![Flying\ Lifter\ v2\label{/FlyingLifterv2}[^source]](/images/FlyingLifterv2.png){ width=489px height=346px}

[^source]:
  Anonymous59 CC-BY-SA Creative Commons [https://commons.wikimedia.org/wiki/File:FlyingLifterv2.png](https://commons.wikimedia.org/wiki/File:FlyingLifterv2.png)



# code

```{python}
import sys

print sys.version
```

# r code



## tibble
The examples are from: https://github.com/tidyverse/tibble.

```{r}
library("tibble")
as_tibble(iris)

tibble(x = 1:5, y = 1, z = x ^ 2 + y)

tribble(
  ~x, ~y,  ~z,
  "a", 2,  3.6,
  "b", 1,  8.5)
```

## ggplot2

The example is from: https://github.com/tidyverse/ggplot2.



```{r fig.cap="Engine displacement and Consumption"}
library("ggplot2")

ggplot(mpg, aes(displ, hwy, colour = class)) + 
  geom_point()
```

## purrr

The example is from: https://github.com/tidyverse/purrr.

```{r}
library("purrr")

mtcars %>%
  split(.$cyl) %>% # from base R
  map(~ lm(mpg ~ wt, data = .)) %>%
  map(summary) %>%
  map_dbl("r.squared")
```

## dplyr

The examples are from: https://cran.rstudio.com/web/packages/dplyr/vignettes/introduction.html.

```{r}
library("dplyr")
library("nycflights13")

filter(flights, month == 1, day == 1)

slice(flights, 1:10)

arrange(flights, year, month, day)

select(flights, year, month, day)

mutate(flights,
  gain = arr_delay - dep_delay,
  speed = distance / air_time * 60)

summarise(flights,
  delay = mean(dep_delay, na.rm = TRUE))
```

# Session information

The R session information for compiling this document is shown below.

```{r session}
sessionInfo()
```
